Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/evaluation.tex
more space savings

Figure~\ref{fig:config-min} shows the size of the configuration generated by \sysname, again as a function of network size. The naive translation of PGIR to ABGP generates extremely large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation.
%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
The figure shows the minimization is highly effective for the data center and backbone policies. In all cases, minimized policies are only a small fraction of the size of their non-minimized counterparts.

>>>>

Figure~\ref{fig:config-min} shows the size of the configuration generated by \sysname, again as a function of network size. The naive translation of PGIR to ABGP generates large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation.
%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
The figure shows that minimization is highly effective for both the data center and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.
